% Insert abstract
\begin{Abstract}
\begin{changemargin}{1cm}{1cm}

The 15-Minute City is an urban planning concept introduced in the last decade, it promotes accessibility with the idea that residents should be able to access basic needs, such as groceries, education, healthcare, and leisure, within a 15-minute travelling time from their homes. The concept aims to provide environmental, social, and economical benefits to society, by reducing the needs of using automobiles, promotes active transportation, and increases the quality of life of residents by providing them with easy access to essential services and amenities. The concept has gained popularity during the COVID-19 pandemic, as it has highlighted the importance of local services and amenities in urban areas.

\vspace{0.5cm}

The concept of the 15-Minute City has been studied in different research fields, including urban planning, transportation, and environmental science. However, there is not a general methodology to determine the areas of a city that can be classified as a 15-Minute City. Most of the existing studies are data driven and focus on specific cities, their solutions are often not algorithmic nor generalised.

\vspace{0.5cm}

The aim of this thesis is to provide a general, adaptive and efficient algorithm to determine the areas of a city that can be classified as a 15-Minute City. A number of existing algorithms on graph data structure are studied, including Breadth-First Search, Dijkstra's algorithm, Johnson's algorithm and some of their variations. The ``15-Minute City algorithm" is then proposed, by combining various ideas and techniques from various algorithms to create a comprehensive and efficient solution that can be used to determine the areas of a city that can be classified as a 15-Minute City.

\end{changemargin}
\end{Abstract}