\subsection{Dijkstra's Algorithm}

The first solution proposed in this thesis is a modified version of Dijkstra's algorithm, which is a well-known algorithm for finding the shortest path between two vertices in a weighted graph. The algorithm works by selecting the node with the smallest distance from the source node and updating the distance of its neighbors. This process is repeated until all vertices have been visited. The algorithm is efficient for finding the shortest path between two vertices in a graph with non-negative edge weights. However, it is not suitable for graphs with negative edge weights.

Adapting the methodogies used by Pezzica et al. \cite{cormen2022introduction}, which incooperate the Dijkstra's algorithm with a (Minimum) Priority Queue data structure. The data structure maintains a dynamic set $S$ of elements, each set element in $S$ has a key and it supports the following dynamic-set operations.

\begin{itemize}
    \item INSERT($S; x; k$): inserts element $x$ with key $k$ into set $S$.
    \item MINIMUM($S$): returns element of $S$ with smallest key.
    \item EXTRACT-MIN($S$): removes and returns element of $S$ with smallest key.
    \item DECREASE-KEY($S;x;k$): decreases value of element $x$’s key to $k$. Assumes $k\leq x$’s current key value.
\end{itemize}

All operations take $O(\log n)$ time in an $n$-element heap with the exception of $\text{MINIMUM}(S)$ being $\Theta(1)$.

We extend the algorithm so that the algotithm will stop once all nodes within $t$ minutes have been visited. As the 15-Minute City concept is primarily used to study cities' characteristics, the input graph of the algorithm is expected to be far larger than each 15 minute area. Therefore, it is necessary to stop the algorithm once all nodes within $t$ minutes have been visited to prevent the algorithm from running indefinitely. The modified algorithm is shown in Algorithm \ref{alg:modified_dijsktra}.

\begin{algorithm}[H]
    \caption{ModifiedDijkstra Algorithm}\label{alg:modified_dijsktra}
    \textbf{Input:} A graph $G(V,E)$, weights $w:E\rightarrow\mathbb{R}_{\geq 0}$, source vertex $s$, \\ \phantom{\textbf{Input:}} time threshold $t$ and $i$ denotes the index of the service type\\
    \textbf{Output} Assign $v.r[i]=1$ for vertices that can reach to source node $s$ within threshold $t$ % Set $S$ of vertices reachable by at most $t$ minutes
    \begin{algorithmic}
        \For {each vertex $v\in V$}
            \State $v.d\gets\infty$
        \EndFor
        \State $s.d\gets 0$
        % \State $S\gets\emptyset$
        \State $Q\gets\emptyset$
        \For {each vertex $v\in V$}
            \State INSERT($Q,v$)
        \EndFor
        \While {$Q\neq\emptyset$}
            \State $v\gets$EXTRACT-MIN$(Q)$
            \If {$v.d>t$}
                \State $Q\gets\emptyset$ \Comment{Break out of While loop}
            \Else
                % \State $S\gets S\cup\{v\}$
                \State $v.r[i] \gets 1 $
                \For {each vertex $u\in Adj[v]$}
                    \If {$u.d>v.d+w(u,v)$}
                        \State $u.d\gets v.d+w(u,v)$
                        \State DECREASE-KEY($Q,u,u.d$)
                    \EndIf
                \EndFor
            \EndIf
        \EndWhile
    \end{algorithmic}
\end{algorithm}

The modified Dijkstra's algorithm shown above only searches for vertices within $t$ minutes from a single source node. For our context of the 15-Minute City, this needs to run for each location of each service type. The full algorithm as the solution of the problem is shown in Algorithm \ref{alg:15mc}.

\begin{algorithm}[H]
    \caption{15-Minute City Algorithm}\label{alg:15mc}
    \textbf{Input:} A graph $G(V,E)$, weights $w:E\rightarrow\mathbb{R}_{\geq 0}$, a time threshold $t$ \\ \phantom{\textbf{Input:}} and a list $S$ of service vertices of $n$ types\\
    \textbf{Output} Set $R\subseteq V$ representing the $t$-Minute City
    \begin{algorithmic}
        \ForAll{vertex $v \in V$}
            \State $v.r \gets \{\mathbf{0}\}^{n}$
            \State $v.l \gets 0$
        \EndFor
        \ForAll{service $v \in S$}
            \State $v.l \gets i^{th}$ type of service
        \EndFor
        \For {each service type $i\in\{1,...,n\}$}
            % \State $S\gets\emptyset$
            \For {each vertex $s$ where $s.l=i$}
                \State $\text{ModifiedDijkstra}(G,w,s,t,i)$
                % \State $S\gets S\cup\text{ModifiedDijkstra}(G,w,s,t,i)$
            \EndFor
            % \For {each vertex $v\in S$}
            %     \State $v.r[i] \gets 1$
            % \EndFor
        \EndFor
        \State $R\gets\emptyset$
        \For {each vertex $v\in V$}
            \If {$v.r = \mathbf{1}$}
                \State $R \gets R\cup \{v\}$
            \EndIf
        \EndFor
    \end{algorithmic}
\end{algorithm}

\subsubsection{Analysis}

\subsection{Dijkstra's Algorithm Revisit}

The second version of the algorithm proposed 

\subsection{All Pairs Shortest Path}